---
title: "The Project"
author: "Victor"
date: "December 17, 2014"
output: html_document
---

First, download the data and load it to R
```{r}
train_raw_data <- read.csv("pml-training.csv")
test_raw_data <- read.csv("pml-testing.csv")
names(train_raw_data)
names(test_raw_data)
```

I find that many columns has NA, so we eliminate the columns that contain any NAs in test_data, and apply it to train_data

```{r}
test_data<-test_raw_data[,-which(apply(test_raw_data,2,function(x)any(is.na(x))))]
train_data<-train_raw_data[,-which(apply(test_raw_data,2,function(x)any(is.na(x))))]
names(train_data)
names(test_data)
names(train_data)==names(test_data)
```

So I get the training and testing data,finally I get train_data and test_data.

```{r}
train_data <- train_data[,8:60]
test_data <- test_data[,8:59]
```



ok, now load the caret and set the seed. In order to analysis my model, i use 20% of data to be training sets and rest of them to be testing sets 

```{r}
library(caret)
set.seed(32323)
inTrain <- createDataPartition(y=train_data$classe,p=0.2,list=FALSE)

train_data_2 <- train_data[inTrain,]
test_data_2 <- train_data[-inTrain,]
```

First, i decided to use `rpart` as the algorithm to devide them apart.
```{r}
modFit <- train(classe ~ .,method = "rpart" ,data= train_data_2)
print(modFit$finalModel)
prediction <- predict(modFit,newdata=test_data_2)
missClass = function(values,prediction){sum(prediction != values)/length(values)}
missClass(test_data_2$classe,prediction)
```

But the miss class rate is high, i expect that the error should be within 5%.
So i use random forest instead.(note: The random forest is relatively slow)

```{r}
modFit2 <- train(classe ~ .,method = "rf" ,data= train_data_2,prox=TRUE)
print(modFit2)
prediction <- predict(modFit2,newdata=test_data_2)
missClass(test_data_2$classe,prediction)
```

As can be seen from the above,the miss class rate is only 0.02574

So i apply it to the test_data of 20 entities, and output them.

```{r}
answer <- predict(modFit2,newdata=test_data)
print(answer)
```

I upload all the answer to the judge, fortunately, it is all right.

